|

### 2021-03-23 appendix/appendix.Rmd
catarina points start

In this section, we present the @weingast1981political theoretical arguments behind the law of 1/n, and their rebuttal by @primo2008distributive. Many of the papers included in this meta-analysis also have their own version of why we need a refined version of the original law of 1/n, but these two papers, in our view, present the most elementary theoretical argument

In their seminal paper, @weingast1981political argue that the number of legislators will increase public spending more than the optimal economic benchmark. Politicians have the incentive to over-provide concentrated benefits to the constituencies, spreading the costs throughout the entire tax pool (all constituencies). The corollary of their suggestion is that larger legislatures generate more expenditure.

In their model, every local public goods project of size $x$ generates a concave benefit $b(x)$ and there are convex costs associated with the project.\footnote{Concave in this case means that $b'>0$ and $b''<0$. Convex in this case mean that $c'>0$ and $c''>0$. We assume that the derivatives are well defined throughout the analysis. Moreover, we drop the constituency index, to facilitate reading the model and because of this, the reader should assume equal constituencies.} The first cost, $c_1(x)$, comprises the expenses within the constituency (e. g., hire a local company to build the project). The second cost, $c_2(x)$, captures the expenses outside the constituency (e. g., hire a company from another state). The third cost $c_3(x)$ captures the externalities generated by the project (e. g., how much prices shift because local economic factors are being used to provide the project). The total cost is then equal to $c(x) = c_1(x) + c_2(x) + c_3(x)$. The tax burden generated by the project is equal to $T(x) = c_1(x) + c_2(x)$.

@@

As the above condition suggests, the law of 1/n holds only in specific situations. @primo2008distributive advances the theory by considering other situations where the law may not hold, and also situations when a reverse prediction of the law of 1/n holds, i. e., larger legislatures leading to lower expenditures. 
Following @primo2008distributive, let $n$ be the number of districts, $m$ the number of citizens in each district, and $nm$ is the total population in the country. Consider a local public good that generates a per capita benefit, according to its size $x$ of $b(x, m) = x^\alpha m^{\beta-1}$, where $\beta$ is the degree of congestion of the public good, i. e. how much the addition of individuals reduce the benefits for other individuals (note that the lower the $\beta$, the higher the congestion). In terms of costs, consider a linear cost $C(x) = x$, and in terms of taxation, assume that the people in the district share taxes between their payments and the central government's. The degree that taxes are shared is denoted by $s$. Moreover, there is a deadweight loss of the taxes $\theta \geq 1$. The tax then becomes: $t = \left(\dfrac{(n – ns + s)x + (ns – s)X}{nm}\right)^\theta$. Collecting terms, the citizens receive the following net benefit of a project with size $x$:

@@

Therefore, there are possibilities for having the law of 1/n in the direction predicted by @weingast1981political, and in a reverse direction, as in @primo2008distributive. Here, we showed the variation changing only the deadweight losses, but there are many other theoretical reasons, such as the limiting power of the upper houses [@malhotra], the XXXX, and XXXX. Most of the literature after @weingast1981political, attempted to find the empirical complements to this original formulation.

>>>>

In this section, we present the law of 1/n as in @weingast1981political, and the refinement proposed by @primo2008distributive. In our view, these two papers present the most theoretically  argument

In their seminal paper, @weingast1981political argue that the number of legislators will increase public spending more than the optimal economic benchmark. Politicians have the incentive to over-provide concentrated benefits to the constituencies, spreading the costs throughout all constituencies. The corollary of their model is that larger legislatures generate more public spending.

In their model, every local public goods project of size $x$ generates a concave benefit $b(x)$, and there are convex costs associated with the project.\footnote{Concave means that $b'>0$ and $b''<0$. Convex means that $c'>0$ and $c''>0$. We assume that the derivatives are well defined throughout the analysis. Moreover, we drop the constituency index, to facilitate reading the model and because of this, the reader should assume that we will always employ a symmetric Nash equilibrium.} The first cost, $c_1(x)$, comprises the expenses within the constituency (e. g., hire a local company to build the project). The second cost, $c_2(x)$, captures the expenses outside the constituency (e. g., hire a company from another state). The third cost $c_3(x)$ captures the externalities generated by the project (e. g., how much prices shift because local economic factors are being used to provide the project). The total cost is then equal to $c(x) = c_1(x) + c_2(x) + c_3(x)$. The tax burden generated by the project is equal to $T(x) = c_1(x) + c_2(x)$.

@@

As the above condition suggests, the law of 1/n holds only in specific situations. @primo2008distributive advances the theory by considering other situations where the law may not hold, and also situations when a reverse prediction of the law of 1/n holds, i. e., larger legislatures leading to lower expenditures.

Following @primo2008distributive, let $n$ be the number of districts, $m$ the number of citizens in each district, and $nm$ is the total population in the country. Consider a local public good that generates a per capita benefit, according to its size $x$ of $b(x, m) = x^\alpha m^{\beta-1}$, where $\beta$ is the degree of congestion of the public good, i. e. how much the addition of individuals reduce the benefits for other individuals (note that the lower the $\beta$, the higher the congestion). In terms of costs, consider a linear cost $C(x) = x$, and in terms of taxation, assume that the people in the district share taxes between their payments and the central government's. The degree that taxes are shared is denoted by $s$. Moreover, there is a deadweight loss of the taxes $\theta \geq 1$. The tax then becomes: $t = \left(\dfrac{(n – ns + s)x + (ns – s)X}{nm}\right)^\theta$. Collecting terms, the citizens receive the following net benefit of a project with size $x$:

@@

Therefore, there are possibilities for having the law of 1/n in the direction predicted by @weingast1981political, and in a reverse direction, as proposed by @primo2008distributive. Here, we showed the variation in deadweight losses, but there are many other theoretical reasons, such as the existence of upper houses [@chen_malhotra_2007], the popular initiatives [@XXXX], and XXXX. Most of the literature after @weingast1981political, focused on complement their original formulation.
